A High-throughput, Scalable Solution for the New York Taxi Trips DEBS Grand Challenge Problem

### 2015-03-30 paper/experiments.tex
fixing some issues

\section{Experiments}
We conducted several experiments to study the scalability of our solution. Firstly we study the throughput and mean message latency variation with the number of \textit{QueryEvaluators} for both single JVM and distributed setups to find the scalability of the parallel evaluation. In an ideal system, we should observe linear throughput increment with a constant message latency. However there are some exceptions and we have provided our explanations on them. Finally we study the throughput variation with the window size to study the suitability of our solution for higher window sizes. All these experiments were performed on a LAN with a network bandwidth of 1Gbps and all machines were Intel(R) Xeon(R) 2.4GHz, 4 core duo machines with 16 GB of memory.

>>>>

\section{Experiments}
We conducted several experiments to study the scalability of our solution. Firstly we study the throughput and mean message latency variation with the number of \textit{QueryEvaluators} for both single JVM and distributed setups to find the scalability of the parallel evaluation. We measured the end to end latency. At the \textit{EventEmitter}, we set the time stamp for all events once the record is read. At the \textit{QueryEvaluator} we copy the original time stamp, if that event causes a top ten value change event. Total delay calculated at the \textit{ResultAggregator} just before writing the event. In an ideal system, we should observe linear throughput increment with a constant message latency. However there are some exceptions and we have provided our explanations on them. Finally we studied the throughput variation with the window size to study the suitability of our solution for higher window sizes. All these experiments were performed on a LAN with a network bandwidth of 1Gbps and all machines were Intel(R) Xeon(R) 2.4GHz, 4 core duo machines with 16 GB of memory.

### 2015-03-30 paper/introduction.tex
fixing some issues

The first query is to find the events which change the top ten routes within last 30 minutes and emit the new route set details along the original event. The given data set contains 899010  routes and the 30 minute time window for this query accounts around 10000 events assuming an equal event distribution. This creates the possibility of processing several thousand route counts specially within peak ours. In other words we need to evaluate several thousand route counts with each event and find 10 top most routes. Similar analysis can be made with profitable cells query as well. In addition to that it requires to  calculate the median fare for each cell.

@@

If we consider an application to process this 173 million data set within an year, it would be a trivial task and any naive implementation satisfy that requirement. However if we consider an application which process these data within minutes, we observe following research challengers.
\begin{enumerate}
	\item \textit{Handling thousands of values in real time :}  An algorithm with O(n) time complexity will not scale for thousands. Therefore is it possible to come up with an algorithm of O(log(n)) time complexity?
	\item \textit{Parallel evaluation :}  This application is not inherently support parallel evaluation. Partitioning route sets and cell sets triggers events for sub sets, but application requires the events with whole sets. Therefore is it possible to partition data and still generate required results to support parallelism?  
\end{enumerate}

@@

We started our work seeking answers for above challengers. First we evaluated doubly linked list and heap based approaches to build a data structure with O(log(n)) time complexity. After several evaluations, we developed a new data structure called \textit{NodeList} which utilizes both concepts. In order to find the running median with O(log(n)) time complexity, we experimented with an algorithm which uses priority queue and the heap data structure we developed. We decided to use former since it gave better performance with smaller window sizes. Then we focused on parallelizing the application and came up with an strategy to aggregate the sub set results to find the final results. As the last step, we conducted several experiments to evaluate our solutions. We repeated this process identifying possible issues and fixing them.

@@

\subsection{Paper Organization}
The remainder of this paper is organized as follows. Section 2 provides an in-depth description about the internal data structures and the algorithms used to process the events. Section 3 describes our scalable design to process events and associated problems. Section 4 proves the soundness of our solution with experimental results. Section 5 discuss the related work including some last year solutions. Section 6 summarizes key concepts and discuss their further applications.

>>>>

The first query is to find the events which change the top ten routes within last 30 minutes and emit the new route set details along the original event. The given data set contains 899010  routes and the 30 minute time window for this query accounts around 10000 events assuming an equal event distribution. This creates the possibility of processing several thousand route counts specially within peak hours. In other words we need to evaluate several thousand route counts with each event and find 10 top most routes. Similar analysis can be made with profitable cells query as well. In addition to that it requires to  calculate the median fare for each cell.

@@

If we consider an application to process this 173 million data set within an year, it would be a trivial task and any naive implementation satisfy that requirement. However if we consider an application which process these data within minutes with minimal latency to process each event, we observe following research challengers.
\begin{enumerate}
	\item \textit{Handling thousands of values in real time :}  An algorithm with O(n) time complexity will not scale for thousands. Therefore is it possible to come up with an algorithm of O(log(n)) time complexity?
	\item \textit{Parallel evaluation :}  This application is not inherently support parallel evaluation. Partitioning route sets and cell sets triggers events for sub sets, but application requires the events with whole sets. Therefore is it possible to partition data and still generate required results to support parallelism?  
\end{enumerate}

@@

We started our work seeking answers for above challengers. First we evaluated doubly linked list and heap based approaches to build a data structure with O(log(n)) time complexity. After several evaluations, we developed a new data structure called \textit{NodeList} which utilizes both concepts. In order to find the running median with O(log(n)) time complexity, we experimented with an algorithm which uses priority queue and the heap data structure we developed. We decided to use former since it gave better performance with smaller window sizes. Then we focused on parallelizing the application and came up with a strategy to aggregate the sub set results to find the final results. As the last step, we conducted several experiments to evaluate the scalability of our solution. We repeated this process identifying possible issues and fixing them.

@@

\subsection{Paper Organization}
The remainder of this paper is organized as follows. Section 2 provides an in-depth description about the internal data structures and the algorithms used to process the events. Section 3 describes our scalable design to evaluate queries and associated problems. Section 4 proves the scalability of our solution with experimental results. Section 5 discuss the related work including some last year solutions. Section 6 summarizes key concepts and discuss their further applications.

### 2015-03-30 paper/paper.tex
fixing meanings
fixing some issues

\title{DBES Grand Challenge : High throughput, scalable solution for processing taxi trip data}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

@@

\maketitle
\begin{abstract}
Processing complex queries on unbounded event streams in real time, is a challenge for many organizational data processing systems. These systems are expected to process data with reduced latency to generate real time events, and high throughput to minimize the required hardware. In this regard, DEBS Grand Challenge 2015 focuses on evaluating two queries (frequent routes and  profitable cells) in real time with low latency and high throughput. These queries involve processing windows of thousands of records. Firstly, such processing demands efficient data structures and algorithms to minimize the processing overhead. Secondly, the system should partition data to process them in parallel to make it scalable.

In this paper, we present a set of data structures which can be used to evaluate the aforementioned queries with O(log(n)) time complexity and a data partitioning technique to process events in parallel. Then we evaluate our solution within signal node as well as in a distributed setting in a commodity cluster of machines over a 1Gbps LAN. We could process frequent routes query with 173 million data set within 5 minutes with less than 4 millisecond latency and profitable cells query with same data set within 11 minutes with less than 5 millisecond latency.
\end{abstract}

@@

\section{Introduction}
%introduction

\input{query_implementation}
\input{query_evaluation}
\input{experiments}
\input{related_work}
%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{paper}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
%APPENDICES are optional
%\balancecolumns
%Appendix A
% That's all folks!
\end{document}

>>>>

\title{A High-throughput, Scalable Solution for the New York Taxi Trips DEBS Grand Challenge Problem}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

@@

\maketitle
\begin{abstract}
Processing complex queries on unbounded event streams in real time, is a challenge for many organizational data processing systems. These systems are expected to process data with reduced latency to generate real time events, and high throughput to minimize the required hardware. In this regard, DEBS Grand Challenge 2015 focuses on evaluating two queries (frequent routes and  profitable cells) in real time with low latency and high throughput. These queries involve processing windows of thousands of records. Firstly, such processing demands efficient data structures and algorithms to minimize the processing overhead. Secondly, the system should partition data to evaluate them in parallel to make it scalable.

In this paper, we present a set of data structures which can be used to evaluate the aforementioned queries with O(log(n)) time complexity and a data partitioning technique to evaluate them in parallel. Then we evaluate our solution in a signal machine as well as in a distributed setting in a commodity cluster of machines over a 1Gbps LAN. We could process frequent routes query with 173 million data set within 5 minutes with less than 4 millisecond latency and profitable cells query with same data set within 11 minutes with less than 5 millisecond latency.
\end{abstract}

@@

\input{introduction}
\input{query_implementation}
\clearpage
\input{query_evaluation}
\input{experiments}
\input{related_work}
\input{conclustion}
%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{paper}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
%APPENDICES are optional
%\balancecolumns
%Appendix A
% That's all folks!
\end{document}

### 2015-03-30 paper/query_evaluation.tex
fixing some issues

We can sequentially execute events either in a single Java Virtual Machine (JVM) or different JVMs (either in one machine or different machines) using TCP sockets to communicate among process instances. Figure \ref{sequential} shows possible executions.

@@

\begin{enumerate}
	\item \textbf{Expired values} : Route count of a particular route can be reduced due to expiration of some events. For an example, lets assume route count for route R1 is 10 and R1 is included in a top ten route event generated by a \textit{QueryEvaluator}. Then lets assume route count for R1 has been reduced to 7 (due to expiration events), when the next event is generated and hence R1 is not included in the next top ten route event. However since R1 value still is in the \textit{ResultAggregator} that may produce an event with this value. To avoid this problem, we send the removed route set details with the top ten route event generated by the \textit{QueryEvaluator}. In that case \textit{ResultAggregator} can first remove those routes.
	\item \textbf{Out of order events} : \textit{ResultAggregator} may receive events in a different order than those are produced at the \textit{EventEmitter}. This out of order events may change the final output of the \textit{ResultAggregator}. We order messages at the \textit{ResultAggregator} to avoid this problem. In order to order messages, we keep a message queue for each \textit{QueryEvaluator} and sent the message with least sequence number to \textit{ResultAggregator},  if a message is present in all queues. 
	\item \textbf{Intermediate top ten route events} : A route event increases the route count for that events' route. Further that can generate some expiration events which may reduce the route count for other routes. The top ten frequent routes can be changed due to these expiration events as well. Lets say in one \textit{QuerayEvaluator} case, a particular event causes two routes R1 and R2 to change and generates a top ten route change event. In the distributed setup these two routes can be in two \textit{QueryEvaluators} and that can cause two top ten route change events. These two events may result in two top ten route change events at \textit{ResultAggregator} as well instead of one. Further we observed only around 5\% of such events are generated, and system goes to the one \textit{QueryEveluator} result after all such event are being executed. Solution for such a problem may depend on the nature in which a real application, uses these results in decision making process. Therefore we could not provide any fix for this problem.
\end{enumerate}

>>>>

We can sequentially execute events either in a single Java Virtual Machine (JVM) or in different JVMs (either in one machine or different machines) using TCP sockets to communicate among process instances. Figure \ref{sequential} shows possible executions.

@@

\begin{enumerate}
	\item \textbf{Expired values} : Route count of a particular route can be reduced due to expiration of some events. For an example, lets assume route count for route R1 is 10 and R1 is included in a top ten route event generated by a \textit{QueryEvaluator}. Then lets assume when the next event is generated, the route count for R1 has been reduced to 7 (due to expiration events) and hence R1 is not included in the next top ten route event. However since R1 value still is in the \textit{ResultAggregator} that may produce an event with this value. To avoid this problem, we send the removed route set details with the top ten route event generated by the \textit{QueryEvaluator}. In that case \textit{ResultAggregator} can first remove those routes.
	\item \textbf{Out of order events} : \textit{ResultAggregator} may receive events in a different order than those are produced at the \textit{EventEmitter}. This out of order events may change the final output of the \textit{ResultAggregator}. We order messages at the \textit{ResultAggregator} to avoid this problem. In order to order messages, we keep a message queue for each \textit{QueryEvaluator} and sent the message with least sequence number to \textit{ResultAggregator},  if a message is present in all queues. 
	\item \textbf{Intermediate top ten route events} : A route event increases the route count for that events' route. Further that can generate some expiration events which may reduce the route count for other routes. The top ten frequent routes can be changed due to these expiration events as well. Lets say in one \textit{QuerayEvaluator} case, a particular event causes two routes R1 and R2 to change and generates a top ten route change event. In the distributed setup these two routes can be in two \textit{QueryEvaluators} and that can cause two top ten route change events. These two events may result in two top ten route change events at \textit{ResultAggregator} as well instead of one. Further we observed only around 5\% of such events are generated, and system goes to the one \textit{QueryEveluator} result after all such event are being executed. Solution for such a problem may depend on the nature in which a real application, uses these results in decision making process. Therefore we could not provide any fix for this problem.
\end{enumerate}

### 2015-03-30 paper/query_implementation.tex
fixing some issues

\section{Query Implementation}
In this section, we elaborate how we have implemented the query logic to achieve O(log(n)) time complexity. The 2015 Grand Challenge problem has two queries. First is to evaluate top ten most frequent routes within the last 30 minutes and second is to evaluate top ten profitable areas within the last 15 minutes. We use a composite object to manage details for each route and fare details to each cell to compare values among routes and cells. However, each time window can have thousands of route and cell details. Therefore, an efficient data structure is required to add, remove, update and retrieve top ten values from a set of objects for a given time window efficiently. Further, since each event is received with route and cell details, the aforementioned operations should be performed using route and cell details as the key. In order to support all these functions with O(log(n)) time complexity we have developed a data structure called \textit{NodeList}. The remaining of this section describes how we have achieve this time complexity with the \textit{NodeList} data structure and how we have implemented the queries using that data structure.

@@

Table \ref{nodelist_api} shows the operations of this data structure. The \textit{NodeValue} is an interface to plug any user defined type as a value. For an example, the route query can use a \textit{RouteCount} object to keep route count while profitable cells query can use \textit{CellProfit} object to keep track of fare details. This interface contains a method called compare to define the order of the values. The \textit{NodeList} data structure provides the notion of a sorted values starting from position 0 (highest value) to its users. The \texttt{decrementPostion} operation moves the corresponding value towards position 0 until the correct position according to sorted order. Therefore this method should be called after increasing the value of an existing object. Similarly \texttt{incrementPosition} operation can be used to move a value to correct position after decreasing the value of an existing object. \texttt{GetTopValues} operation returns the top ten values of the list. The query algorithm sections further elaborate usage of these methods.

@@

\subsection{Finding Runtime Median}
In general, we can find runtime median using two heaps. One to keep values greater than the current median and one to keep values less than the current median. An implement of this algorithm using two \textit{java.util.PriorityQueue}s have an O(log(n)) time complexity for add operation and O(n) time complexity for remove operation (\texttt{delete} operation of \textit{java.util.PriorityQueue} takes O(n) time).  We overcame this issue using \textit{DynamicHeap} to keep values. In our solution, we use value as the key to insert and delete from the \textit{DynamicHeap} and keep value with its count (same value can be repeated) in the \textit{DynamicHeap}. In worst case it has O(log(n)) time complexity for both add and remove operations and in best case (i.e value already present and that does not cause median change) it has O(1) time complexity.

@@

The frequent route query entails finding the most frequent routes within the last 30 minutes. Algorithm \ref{frequent_route_algorithm} shows the algorithm to process this query using the \textit{NodeList} data structure and a queue to keep the events for the time window.  Since queue operations are supported in O(1) time, query evaluations happen in O(log(n)) time. Algorithm \ref{frequent_route_algorithm} shows the basic algorithm to process an event. This algorithm assumes there is a global \textit{NodeList} object and route counts are stored in an object called \textit{RouteCount}.

@@

Processing an event can cause add, remove or update values of the existing time window objects. Therefore query processing mainly involves performing the above operations with the underlying \textit{NodeList} data structure and comparing top ten routes before and after. As shown in Algorithm \ref{frequent_route_algorithm}, when an event arrives, first it puts the event to time window to keep track for last 30 minutes. Then it adds new route value or updates the existing value and moves its position. Similarly, for expired events either it removes the values or reduces the count for existing values. Finally, two lists are compared to decide whether to generate an event or not. Here we have given a rough outline of the algorithm. Real implementation considers other factors such as sequence number to order events.

@@

We have implemented profitable cells query in a similar manner to the frequent route query using  time windows. Complexity of the query raised following issues and we have solved them as given below.
\begin{enumerate}
	\item The profitability is calculated using the median profit and the number of empty taxis. In order to calculate median, we use \textit{java.util.PriorityQueue} based approach mentioned in (Section 2.4). We choose this option over our implementation, because this approach performs better with smaller window sizes. First, these heap sizes do not grow over 145 and there are same values repeating in the list increasing the probability of finding a value without traversing the whole list. Secondly, our implementation create more objects per operation compared to just keeping double values though the time complexity is O(log(n)). In section 4.3 we show that our approach works better for larger window sizes.
	\item In order to keep track of empty taxis, we need to process both pickup cell and dropoff cell details for each message. One way of doing this is to send all events for the same process instance and process both details with one event. However this avoids the possibility of partitioning data across different processes. We generate two events, one for pickup data and one for dropoff data to make the process parallel. 
	\item In order to handle expiration of dropoff events, we keep track of the taxi ids currently available in a particular cell. If a pickup event occurs before dropoff event expiration, then we remove that taxi id from that cell and reduce the empty taxi count. In such a case, dropoff event expiration does not cause a reduction of taxi count.
\end{enumerate}

>>>>

\section{Query Implementation}
In this section, we elaborate how we have implemented the query logic to achieve O(log(n)) time complexity. The 2015 Grand Challenge problem has two queries. First is to evaluate top ten most frequent routes within the last 30 minutes and second is to evaluate top ten profitable areas within the last 15 minutes. We can use composite objects to manage details for each route and cell and compare them to find top 10 values. However, each time window can have thousands of route and cell details. Therefore, an efficient data structure is required to add, remove, update and retrieve top ten values from a set of objects for a given time window efficiently. Further, since each event is received with route and cell details, the aforementioned operations should be performed using route and cell details as the key. In order to support all these functions with O(log(n)) time complexity we have developed a data structure called \textit{NodeList}. The remaining of this section describes how we have achieved this time complexity with the \textit{NodeList} data structure and how we have implemented the queries using that data structure.

@@

Table \ref{nodelist_api} shows the operations of this data structure. The \textit{NodeValue} is an interface to plug any user defined type as a value. For an example, the route query can use a \textit{RouteCount} object to keep route count while profitable cells query can use \textit{CellProfit} object to keep track of fare details. This interface contains a method called \texttt{compare} to define the order of the values. The \textit{NodeList} data structure provides the notion of a sorted values starting from position 0 (highest value) to its users. The \texttt{decrementPostion} operation moves the corresponding value towards position 0 until the correct position according to sorted order. Therefore this method should be called after increasing the value of an existing object. Similarly \texttt{incrementPosition} operation can be used to move a value to correct position after decreasing the value of an existing object. \texttt{GetTopValues} operation returns the top ten values of the list. The query algorithm sections further elaborate usage of these methods.

@@

\subsection{Finding Runing Median}
In general, we can find runing median using two heaps. One to keep values greater than the current median and one to keep values less than the current median. An implement of this algorithm using two \textit{java.util.PriorityQueue}s have an O(log(n)) time complexity for add operation and O(n) time complexity for remove operation (\texttt{remove} operation of \textit{java.util.PriorityQueue} takes O(n) time).  We overcame this issue using \textit{DynamicHeap} to keep values. In our solution, we use value as the key to insert and delete from the \textit{DynamicHeap} and keep value with its count (same value can be repeated) in the \textit{DynamicHeap}. In worst case it has O(log(n)) time complexity for both add and remove operations and in best case (i.e value already present and that does not cause median change) it has O(1) time complexity.

@@

The frequent route query entails finding the most frequent routes within the last 30 minutes. Algorithm \ref{frequent_route_algorithm} shows the algorithm to process this query using the \textit{NodeList} data structure and a queue to keep the events for the time window.  Since queue operations are supported in O(1) time, query evaluations happen in O(log(n)) time. Algorithm \ref{frequent_route_algorithm} shows the basic algorithm to evaluate the query an event. This algorithm assumes there is a global \textit{NodeList} object and route counts are stored in an object called \textit{RouteCount}.

@@

Each query evaluation can cause add, remove or update values of the existing time window objects. Therefore query processing mainly involves performing the above operations with the underlying \textit{NodeList} data structure and comparing top ten routes before and after. As shown in Algorithm \ref{frequent_route_algorithm}, when an event arrives, first it puts the event to time window to keep track for last 30 minutes. Then it adds new route value or updates the existing value and moves its position. Similarly, for expired events either it removes the values or reduces the count for existing values. Finally, two lists are compared to decide whether to generate an event or not. Here we have given a rough outline of the algorithm. Real implementation considers other factors such as sequence number to order events.

@@

We have implemented profitable cells query in a similar manner to the frequent route query using  time windows. Complexity of the query raised following issues and we have solved them as given below.
\begin{enumerate}
	\item The profitability is calculated using the median profit and the number of empty taxis. In order to calculate median, we use \textit{java.util.PriorityQueue} based approach mentioned in (Section 2.4). We choose this option over our implementation, because this approach performs better with smaller window sizes. First, these heap sizes do not grow over 145 and there are same values repeating in the list increasing the probability of finding a value without traversing the whole list. Secondly, our implementation creates more objects per operation compared to just keeping double values though the time complexity is O(log(n)). In section 4.3 we show that our approach works better for larger window sizes.
	\item In order to keep track of empty taxis, we need to process both pickup cell and dropoff cell details for each message. One way of doing this is to send all events for the same process instance and process both details with one event. However this avoids the possibility of partitioning data across different processes. We generate two events, one for pickup data and one for dropoff data to make the process parallel. 
	\item In order to handle expiration of dropoff events, we keep track of the taxi ids currently available in a particular cell. If a pickup event occurs before dropoff event expiration, then we remove that taxi id from that cell and reduce the empty taxi count. In such a case, dropoff event expiration does not cause a reduction of taxi count.
\end{enumerate}

### 2015-03-30 paper/related_work.tex
fixing meanings
fixing some issues

\section{Related work}
DEBS Grand Challenge problem naturally fallen into distributed stream processing domain. Many such systems have been developed with different feature sets according to the applications they use. Yahoo S4 \cite{neumeyer2010s4} is used at Yahoo to calculate the click through rate, Twitter Storm \cite{toshniwal2014storm} is used in Twitter to process tweets, MillWheel \cite{akidau2013millwheel} is used at Google to track trends in web queries. All these systems are based on the Actor model \cite{agha1985actors} and provide a generic API to implement logic to process data. Apart from basic communication these frameworks provides other features such as reliable message delivery, state persistence dynamic membership management. Spark stream \cite{zaharia2012discretized} provides fault tolerance based on its Resilient Distributed Datasets RDDs \cite{zaharia2012resilient} and Muppet \cite{lam2012muppet} provides state persistence using a \textless key, value\textgreater store based on Cassandra \cite{lakshman2010cassandra}.

>>>>

\section{Related work}
DEBS Grand Challenge problem naturally fallen into distributed stream processing domain. Many such systems have been developed with different feature sets according to the applications they use. Yahoo S4 \cite{neumeyer2010s4} is used at Yahoo to calculate the click through rate, Twitter Storm \cite{toshniwal2014storm} is used in Twitter to process tweets, MillWheel \cite{akidau2013millwheel} is used at Google to track trends in web queries. All these systems are based on the Actor model \cite{agha1985actors} and provide a generic API to implement logic to process data. Apart from basic communication these frameworks provides other features such as reliable message delivery, state persistence and dynamic membership management.
